Community comparison

### 2019-12-28 code/community.Rmd
minor

stacked_bar +
  theme(legend.position="none")
#18s: check
# cellct: _
# rbcl: _
# red green colorblind similatur
```

stacked bar legend
```{r}
legend <- stacked_bar %>% cowplot::get_legend()
grid.newpage()
grid.draw(legend)
```

@@

>>>>

stack_no_legend <- stacked_bar +
  theme(legend.position="none")
#18s: check
# cellct: _
# rbcl: _
# red green colorblind similatur
```

stacked bar legend
```{r}
legend <- stacked_bar %>% 
  cowplot::get_legend() %>% 
  ggpubr::as_ggplot()
legend
```

@@

ggsave(here::here("manuscript/figs/stack.pdf"), plot=stack_no_legend, width=7, height=5)
ggsave(here::here("manuscript/figs/stack_legend.pdf"), plot=legend, width=7, height=5)
